### 2024-11-01 paper/paper.qmd
paper updated
paper updated

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false
#### Workspace setup ####
library(tidyverse)
library(knitr)
library(dplyr)
library(arrow)
set.seed(912)
#### Read data ####
raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
train_Trump <- read_parquet(here::here("data/02-analysis_data/01-training/train_Trump.parquet"))
train_Harris <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
Trump_model <- readRDS(here::here("models/Trump_model.rds"))
Harris_model <- readRDS(here::here("models/Harris_model.rds"))
```

# Introduction

# Data {#sec-data}

## Overview

## Raw data
```{r}
# Identify variables (columns) that are completely empty (all NA values)
empty_variables <- names(raw_data)[sapply(raw_data, function(x) all(is.na(x)))]

# Print the names of empty variables
print(empty_variables)
```

```{r}
names(raw_data)
```

Raw data 一共包含了52个variable以及17133个sample。52个varibles中以下几个与我们的project明显无关，我们在此不做讨论：
```{r}
# 这里需要画一个table，展示无关变量
del_1 <- c("notes", "url", "url_article", "url_topline", "url_crosstab", "source")
droped_data <- raw_data %>% select(-any_of(del_1))
names(droped_data)
```
此外，还有一些相同的variables，我们保留其一，剩下的也不做讨论，它们包括：
```{r}
# 这里需要画一个table，展示删除的重复变量
del_2 <- c("pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name",
           "population_full", "candidate_id", "candidate_name")
droped_data <- droped_data %>% select(-any_of(del_2))
names(droped_data)
```
此外，在已知我们分析的是美国总统竞选的前提下，我们删除以下variables：
```{r}
# 这里需要画一个table，展示以知变量
del_3 <- c("office_type", "seat_number", "seat_name")
droped_data <- droped_data %>% select(-any_of(del_3))
names(droped_data)
```
常数变量我们也不做讨论，因为无法影响我们的预测，它们是：
```{r}
# Identify variables where all values are the same (including NA)
same_value_variables <- names(droped_data)[sapply(droped_data, function(x) length(unique(x)) == 1)]
# Create a data frame with variables and their unique values
same_value_data <- data.frame(Variable = same_value_variables, Value = sapply(same_value_variables, function(var)
unique(na.omit(droped_data[[var]]))[1]))
# Print the names of variables with all identical values using kable
kable(same_value_data, col.names = c("Variable", "Value"))
```
```{r}
del_4 <- c("endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch")
droped_data <- droped_data %>% select(-any_of(del_4))
names(droped_data)
```
其中categorical的有
```{r}
catego <- c("poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state", "start_date", "end_date",
         "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "population", "tracking", "created_at", "internal",
         "partisan","race_id", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical","party","answer")
```
重要的categorical为下面的，剩下的将在appendix阐述
```{r}
catego_inp <- c("poll_id", "methodology", )
```

以及numerical的variables
```{r}
muner <- droped_data %>% select(-any_of(catego))
names(muner)
```

## Cleaned data

## Measurement

## Similar dataset

# Model

## Model set-up

## Model validation

```{r, fig.width=10, fig.height=10}
data2 = raw_data %>% select("pollscore","transparency_score","sample_size")
pairs( data2 , main = "Predictor vs predictor")
```

```{r}
par(mfrow=c(2,2))
plot(Trump_model,1)
plot(Trump_model,2)

```

## Predictor variables

### 2024-11-01 scripts/05-exploratory_data_analysis.qmd
paper updated
paper updated

#### Preamble ####
# Purpose: Models... [...UPDATE THIS...]
# Author: Rohan Alexander [...UPDATE THIS...]
# Date: 11 February 2023 [...UPDATE THIS...]
# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
# License: MIT
# Pre-requisites: [...UPDATE THIS...]
# Any other information needed? [...UPDATE THIS...]

```{r}
#### Workspace setup ####
library(tidyverse)
library(rstanarm)

#### Read data ####
analysis_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
```

```{r}
# Check for missing values in each column
missing_values <- sapply(analysis_data, function(x) sum(is.na(x)))
print(missing_values)
```

```{r}
# Get unique pollster IDs
unique_pollster_ids <- unique(analysis_data$pollster_id)
print(unique_pollster_ids)
```
```{r}
# Get unique question IDs
unique_question_ids <- unique(analysis_data$question_id)
print(unique_question_ids)
```
```{r}
unique_question_ids_str <- paste(unique(unique_question_ids), collapse = ",")
print(unique_question_ids_str)
```

```{r}
View(unique_question_ids_str)
```

```{r}
# Get the maximum and minimum values of numeric_grade
max_numeric_grade <- max(analysis_data$numeric_grade, na.rm = TRUE)
min_numeric_grade <- min(analysis_data$numeric_grade, na.rm = TRUE)
print(paste("Maximum numeric grade:", max_numeric_grade))
print(paste("Minimum numeric grade:", min_numeric_grade))
```

```{r}
# Plot histogram of numeric_grade
ggplot(analysis_data, aes(x = numeric_grade)) +
  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
  theme_minimal() +
  labs(title = "Histogram of Numeric Grade", x = "Numeric Grade", y = "Count")
```
```{r}
# Plot histogram of pollscore
ggplot(analysis_data, aes(x = pollscore)) +
  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
  theme_minimal() +
  labs(title = "Histogram of pollscore", x = "pollscore", y = "Count")
```
```{r}
# Get unique methodologys
unique_methodologys <- unique(analysis_data$methodology)
print(unique_methodologys)
```
```{r}
# Plot histogram of transparency_score
ggplot(analysis_data, aes(x = transparency_score)) +
  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
  theme_minimal() +
  labs(title = "Histogram of transparency_score", x = "transparency_score", y = "Count")
```
```{r}
# Find the earliest start date and the latest end date
earliest_start_date <- min(analysis_data$start_date, na.rm = TRUE)
latest_end_date <- max(analysis_data$end_date, na.rm = TRUE)
print(paste("Earliest start date:", earliest_start_date))
print(paste("Latest end date:", latest_end_date))
```

```{r}
# Plot histogram of sample_size
ggplot(analysis_data, aes(x = sample_size)) +
  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
  theme_minimal() +
  labs(title = "Histogram of sample_size", x = "sample_size", y = "Count")
```
```{r}
# Get unique population
unique_population <- unique(analysis_data$population)
print(unique_population)
```
```{r}
# Get unique race_id
unique_race_id <- unique(analysis_data$race_id)
print(unique_race_id)
```

```{r}
unique_race_id_str <- paste(unique(unique_race_id), collapse = ",")
clipr::write_clip(unique_race_id_str)
```

```{r}
# Get unique stage
unique_stage <- unique(analysis_data$stage)
print(unique_stage)
```

```{r}
# Get unique stage
unique_nationwide_batch <- unique(analysis_data$nationwide_batch)
print(unique_nationwide_batch)
```

```{r}
# Get unique ranked_choice_reallocated
unique_ranked_choice_reallocated <- unique(analysis_data$ranked_choice_reallocated)
print(unique_ranked_choice_reallocated)
```

```{r}
# Get unique hypothetical
unique_hypothetical <- unique(analysis_data$hypothetical)
print(unique_hypothetical)
```
```{r}
# Calculate the ratio of FALSE to TRUE in the hypothetical column
hypothetical_ratio <- table(analysis_data$hypothetical)
print(hypothetical_ratio)
false_to_true_ratio <- hypothetical_ratio["FALSE"] / hypothetical_ratio["TRUE"]
print(paste("False to True Ratio:", false_to_true_ratio))
```

```{r}
# Get unique party
unique_party <- unique(analysis_data$party)
print(unique_party)
```

```{r}
# Get unique population
unique_population <- unique(analysis_data$population)
print(unique_population)
```

>>>>

#### Preamble ####
# Purpose: Explore the analysis data and find representitive values
# Author: Haowei Fan, Fangning Zhang, Shaotong Li
# Date: 13 October 2024
# Contact: haowei.fan@mail.utoronto.ca
# License: MIT
# Pre-requisites: 02-analysis_data saved and loaded
# Any other information needed? None

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Workspace setup ####
library(tidyverse)
library(rstanarm)
library(patchwork)
raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Get unique pollster IDs
unique_pollster_ids <- unique(raw_data$pollster_id)
print(unique_pollster_ids)
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Get unique question IDs
unique_question_ids <- unique(raw_data$question_id)
print(unique_question_ids)
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Get unique methodologys
unique_methodologys <- unique(raw_data$methodology)
print(unique_methodologys)
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Get unique population
unique_population <- unique(raw_data$population)
print(unique_population)
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Get unique race_id
unique_race_id <- unique(raw_data$race_id)
print(unique_race_id)
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Get unique ranked_choice_reallocated
unique_ranked_choice_reallocated <- unique(raw_data$ranked_choice_reallocated)
print(unique_ranked_choice_reallocated)
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Get unique hypothetical
unique_hypothetical <- unique(raw_data$hypothetical)
print(unique_hypothetical)
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Get unique party
unique_party <- unique(raw_data$party)
print(unique_party)
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Get the maximum and minimum values of numeric_grade
max_numeric_grade <- max(raw_data$numeric_grade, na.rm = TRUE)
min_numeric_grade <- min(raw_data$numeric_grade, na.rm = TRUE)
print(paste("Maximum numeric grade:", max_numeric_grade))
print(paste("Minimum numeric grade:", min_numeric_grade))
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Find the earliest start date and the latest end date
earliest_start_date <- min(raw_data$start_date, na.rm = TRUE)
latest_end_date <- max(raw_data$end_date, na.rm = TRUE)
print(paste("Earliest start date:", earliest_start_date))
print(paste("Latest end date:", latest_end_date))
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Calculate the ratio of FALSE to TRUE in the hypothetical column
hypothetical_ratio <- table(raw_data$hypothetical)
print(hypothetical_ratio)
false_to_true_ratio <- hypothetical_ratio["FALSE"] / hypothetical_ratio["TRUE"]
print(paste("False to True Ratio:", false_to_true_ratio))
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Find the range of pollscore in the original dataset
pollscore_range <- range(raw_data$pollscore, na.rm = TRUE)
print(paste("Pollscore range:", pollscore_range[1], "to", pollscore_range[2]))
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Plot histogram of numeric_grade
ggplot(raw_data, aes(x = numeric_grade)) +
  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
  theme_minimal() +
  labs(title = "Histogram of Numeric Grade", x = "Numeric Grade", y = "Count")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Plot histogram of pollscore
ggplot(raw_data, aes(x = pollscore)) +
  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
  theme_minimal() +
  labs(title = "Histogram of pollscore", x = "pollscore", y = "Count")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Plot histogram of transparency_score
ggplot(raw_data, aes(x = transparency_score)) +
  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
  theme_minimal() +
  labs(title = "Histogram of transparency_score", x = "transparency_score", y = "Count")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Plot histogram of sample_size
ggplot(raw_data, aes(x = sample_size)) +
  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
  theme_minimal() +
  labs(title = "Histogram of sample_size", x = "sample_size", y = "Count")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Find the top 3 candidates.
candidate_ranking <- raw_data %>%
  group_by(candidate_name) %>%
  summarize(
    poll_count = n(),                    
    avg_weighted_pct = mean(poll_count * pct, na.rm = TRUE)  
  ) %>%
  arrange(desc(avg_weighted_pct)) %>%    
  slice_head(n = 3)                       
print(candidate_ranking)
```
